### 2020-08-01 cases_and_policies/rmd/regressionsWithPlots.Rmd

```{r caseregs, cache=FALSE, warning=FALSE, results='hide'}
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national")) #,
#c("dlogdc", "logdc"))
#infovars2 <- list(c( "logdc"))
tvars <- "dlogtests"  
# xlist <-list("party", "party") 
# xlist <-list(c("party","logvote"), c("party","logvote")) 
xlist <- list("","")
interactions <-list("month", statevars)
ilist <- list(interactions, interactions)
iv <- list("0","0") #,"(testratedc ~ lag(testratedc,14))")

@@

#df$pindex <- (df$pshelter+df$pmovie+df$prestaurant+df$pnonessential)/4
df$pindex <- (df$pshelter+df$prestaurant+df$pnonessential)/3

yvar <- "dlogdc"
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national"))
tvars <- "dlogtests"  
L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
for (k in 1:length(infovars)) { 
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars), 0, L, "state + month")
  piy[[(1+4*(k-1))]] <- m
  #m$reg$coefficients[1:(9+2*(k-1))] <- m$bc2[1:(9+2*(k-1))] 
  m$reg$beta[1:(9+2*(k-1))] <- m$bc2[1:(9+2*(k-1))] 
  # m$reg$tval <- m$reg$beta/m$reg$se
  # m$reg$rpval <- pnorm(-abs(m$reg$beta), sd=m$reg$se)
  piy[[(2+4*(k-1))]] <- m
  pols <- c("pmaskbus","pk12","pindex") 
  # pols <- c("pmaskbus","pk12","pmovie","pindex") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars), 0, L, "state + month")
  piy[[(3+4*(k-1))]] <- m 
  #m$reg$coefficients[1:(6+2*(k-1))] <- m$bc2[1:(6+2*(k-1))] 
  m$reg$beta[1:(6+2*(k-1))] <- m$bc2[1:(6+2*(k-1))]
  # m$reg$tval <- m$reg$beta/m$reg$se
  # m$reg$pval <- pnorm(-abs(m$reg$beta), sd=m$reg$se) 
  #m$reg$beta[1:(5+2*(k-1))] <- m$bc[1:(5+2*(k-1))] 
  piy[[(4+4*(k-1))]] <- m 
}

colnames(piy[[1]]$reg$response) <- "dlogdc"  
showhtmltables(NULL, NULL,  piy);
prefix="cases-fe"
#savetextables(NULL, NULL, piy[1:4], prefix="cases-fe")
   ylbl <- colnames(piy[[1]]$reg$response)
    if (ylbl=="dlogdd") ylbl <- "Death Growth"
    if (ylbl=="dlogdc") ylbl <- "Case Growth"

@@

yvar <- "dlogdd"
infovars <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national")) 
L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list() 
for (k in 1:length(infovars)) { 
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              sprintf("lag(%s, %d)", infovars[[k]], L), 0, L, "state + month")
  piy[[(1+4*(k-1))]] <- m
  m$reg$beta[1:(8+2*(k-1))] <- m$bc2[1:(8+2*(k-1))] 
  #m$reg$beta[1:(5+2*(k-1))] <- m$bc[1:(5+2*(k-1))] 
  # m$reg$tval <- m$reg$beta/m$reg$se
  # m$reg$pval <- pnorm(-abs(m$reg$beta), sd=m$reg$se)
  piy[[(2+4*(k-1))]] <- m
  pols <- c("pmaskbus","pk12","pindex") 
  #pols <- c("pmaskbus","pk12","pmovie","pindex") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              sprintf("lag(%s, %d)", infovars[[k]], L), 0, L, "state + month")
  piy[[(3+4*(k-1))]] <- m 
  m$reg$beta[1:(5+2*(k-1))] <- m$bc2[1:(5+2*(k-1))] 
  #m$reg$beta[1:(4+2*(k-1))] <- m$bc[1:(4+2*(k-1))] 
  # m$reg$tval <- m$reg$beta/m$reg$se
  # m$reg$pval <- pnorm(-abs(m$reg$beta), sd=m$reg$se) 
  piy[[(4+4*(k-1))]] <- m
}

>>>>

```{r caseregs, cache=FALSE, warning=FALSE, results='hide'}
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national")) #,
#c("dlogdc", "logdc"))
#infovars2 <- list(c( "logdc"))
tvars <- "dlogtests"
xlist <-list("", "")
interactions <-list("month", statevars)
ilist <- list(interactions, interactions)
iv <- list("0","0") #,"(testratedc ~ lag(testratedc,14))")

@@

df$pindex <- (df$pshelter+df$pmovie+df$prestaurant+df$pnonessential)/4
#df$pindex <- (df$pshelter+df$prestaurant+df$pnonessential)/3

yvar <- "dlogdc"
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national"))
tvars <- "dlogtests"
L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()

#' Update the coefficients of felm object.  Also updates the t stats
#' and p values, so that summary and stargazer work correctly after.
replacecoef <- function(reg, newcoef) {
  reg$beta[] <- newcoef
  reg$coefficients[] <- newcoef
  reg$tval <- reg$beta/reg$se
  reg$pval <- pt(-abs(reg$tval),df=reg$df)*2
  reg$rtval <- reg$beta/reg$rse
  reg$rpval <- pt(-abs(reg$rtval),df=reg$df)*2
  reg$ctval <- reg$beta/reg$cse
  reg$cpval <- pt(-abs(reg$ctval),df=reg$df)*2
  return(reg)
}

for (k in 1:length(infovars)) {
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential")
  m <-  reg_fe(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars), 0, L, "state + month")
  piy[[(1+4*(k-1))]] <- m
  m$reg <- replacecoef(m$reg, m$bc2)
  piy[[(2+4*(k-1))]] <- m
  pols <- c("pmaskbus","pk12","pindex")
  m <-  reg_fe(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars), 0, L, "state + month")
  piy[[(3+4*(k-1))]] <- m
  m$reg <- replacecoef(m$reg, m$bc2)
  piy[[(4+4*(k-1))]] <- m
}

showhtmltables(NULL, NULL,  piy);
prefix="cases-fe"
#savetextables(NULL, NULL, piy[1:4], prefix="cases-fe") copying and

# pasting this is bad style and seems like it might create maintenance
# problems ...
   ylbl <- colnames(piy[[1]]$reg$response)
    if (ylbl=="dlogdd") ylbl <- "Death Growth"
    if (ylbl=="dlogdc") ylbl <- "Case Growth"

@@

yvar <- "dlogdd"
infovars <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national"))
L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
for (k in 1:length(infovars)) {
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential")
  m <-  reg_fe(sdf, yvar, pols, NULL,
              sprintf("lag(%s, %d)", infovars[[k]], L), 0, L, "state + month")
  piy[[(1+4*(k-1))]] <- m
  m$reg <- replacecoef(m$reg, m$bc2)
  piy[[(2+4*(k-1))]] <- m
  pols <- c("pmaskbus","pk12","pindex")
  m <-  reg_fe(sdf, yvar, pols, NULL,
              sprintf("lag(%s, %d)", infovars[[k]], L), 0, L, "state + month")
  piy[[(3+4*(k-1))]] <- m
  m$reg <- replacecoef(m$reg, m$bc2)
  piy[[(4+4*(k-1))]] <- m
}
